### 2019-06-30 papers/journal/intro.tex
minor update

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT,  SMT and QBF solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%

In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations were modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle system with just 8 compartments).
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper we call it universal condition) was partly handled using sampling and left open as a future work.
%
In this paper we present both the SMT and QBF encoding to address these two problems.
%
%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
%\subsection{Previous work and our Contribution}
%
%The following are the contributions of this work:
%\begin{itemize}
%	\item We have added novel encoding reachability and 3-4 connectivity
%	\item Direct encoding into the SAT solver
%	\item A user friendly and scalable tool based on well known SMT solver Z3
%\end{itemize}

\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool upto the size that makes tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

>>>>

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT,  SMT, and QBF solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle the system with just 8 compartments).
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled using sampling and left open as future work.
%
In this paper, we present both the SMT and QBF encodings to address these two problems.
%
%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
%\subsection{Previous work and our Contribution}
%
%The following are the contributions of this work:
%\begin{itemize}
%	\item We have added novel encoding reachability and 3-4 connectivity
%	\item Direct encoding into the SAT solver
%	\item A user friendly and scalable tool based on well known SMT solver Z3
%\end{itemize}

\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool to the size that makes the tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
